### 2015-07-08 narrative/data-reduction.tex
spelling, etc. changes

Our previous
work~\cite{lakshminarasimhan2011compressing,lakshminarasimhan2011compressing,%
gong2012multi,jenkins2012byte,gong2013parlo,boyuka2014transparent,%
tang2014improving}
has focused on several alternative techniques to not only reduce the data
but also re-organize the data. Previously we have examined:

@@

We will also research the time it takes to re-organize the data and use the
multi-layer approach to staging to understand where the data gets reduced and
where it gets re-organized. Open questions are: 1) do we move the data over to
other nodes to then reduce and re-organize, 2) do we first reduce the data and
then later re-organize this data on different nodes?  3) do we use different
cores on a node to do data-refactoring.  Similarly we will examine the cost of
reading the data. It is clear that if we only read in the high-importance data
it should improve the overall time to move the data from the SSIO layer to the
application, but what happens when users want all of the data? There is an
obvious penalty of having to take data in a hierarchical layout and then place
this back to a single-layer view.  Additional research questions which must be
addressed: Will some types of data (PIC data, finite element data, ...) be
conducive  for data-refactoring than others? How much semantic-domain knowledge
will we need to get a dramatic improvement of the storage system over not doing
anything special?

We will measure these methods using the fusion XGC simulation and the
corresponding analysis routines which they use for their largest simulations.
We will also work with Jeroen Tromp's SPECFM3D~\cite{SPECFEM3D} code, and the
fusion GTC~\cite{klasky2003grid} code.  In all cases we will measure their
impact from their current simulations, and their projected simulations and
analytics on exascale machines. Since all three of these codes are part of the
OLCF CAAR~\cite{CAAR} project for early access, there is strong belief that the
simulations will be close to exascale simulations and we will be able to run
these on prototypes of our SSIO layer to examine the full impact of
data-refactoring.

>>>>

Our previous
work~\cite{lakshminarasimhan2011compressing,%
gong2012multi,jenkins2012byte,gong2013parlo,boyuka2014transparent,%
tang2014improving}
has focused on several alternative techniques to not only reduce the data
but also re-organize the data. Previously we have examined:

@@

We will also research the time it takes to re-organize the data and use the
multi-layer approach to staging to understand where the data gets reduced and
where it gets re-organized. Open questions are: 1) do we move the data over to
other nodes to then reduce and re-organize, 2) do we first reduce the data and
then later re-organize this data on different nodes?  3) do we use different
cores on a node to do data-refactoring.  Similarly we will examine the cost of
reading the data. It is clear that if we only read in the high-importance data
it should improve the overall time to move the data from the SSIO layer to the
application, but what happens when users want all of the data? There is an
obvious penalty of having to take data in a hierarchical layout and then place
this back to a single-layer view.  Additional research questions which must be
addressed: Will some types of data (e.g. PIC data) be more
conducive  for data-refactoring than others? How much semantic-domain knowledge
will we need to get a dramatic improvement of the storage system over not doing
anything special?

We will measure these methods using the fusion XGC simulation and the
corresponding analysis routines which they use for their largest simulations.
We will also work with the SPECFM3D~\cite{SPECFEM3D} code, and the
fusion GTC~\cite{klasky2003grid} code.  In all cases we will measure their
impact from their current simulations, and their projected simulations and
analytics on exascale machines. Since all three of these codes are part of the
OLCF CAAR~\cite{CAAR} project for early access, there is strong belief that the
simulations will be close to exascale simulations and we will be able to run
these on prototypes of our SSIO layer to examine the full impact of
data-refactoring.
